---
title: "My R Markdown Primer"
author: "Avery Lane"
date: "2025-11-10"
output: html_document
---

## R Markdown

An R Markdown is a simple formatting syntax for documents such as HTML, PDF, and Word. It is helpful because it lets you mix narrative text, executable R code, and math in one file, then “knit” it into a shareable document. It supports reproducible analysis because the output is generated directly from the source code and data.

## Markdown Text - Narrative Paragraph

R Markdown is one of my favorite tools to use because it keeps everything in one organized place. I like how it lets me combine text, code, and visuals without having to switch between multiple programs. For this assignment, I created a simple document that includes text, math, and code chunks using the ggplot2 package and the built-in mtcars dataset. The goal was to practice writing in Markdown format, run basic R code, and knit it into an HTML report.

## LaTeX Equation

$m = \frac{y_2 - y_1}{x_2 - x_1$


$$
m = \frac{y_2 - y_1}{x_2 - x_1}
$$

## Code Chunk 1: Load Library/Dataset

```{r setup}

# Load Library
library(ggplot2)

# Call Data
data(mtcars)

```

## Code Chunk 2: Run Analysis or Generate Plot

```{r cars}

# Plot Data
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point()

```

## Reflection

I actually enjoy working in R Markdown and use it pretty regularly for another class, so this assignment felt natural to me. I think it’s a super helpful tool because it keeps my work neat and organized while letting me explain my thought process right next to the code. I also like how easy it is to knit a clean, professional-looking report that includes both explanations and results. It makes it much easier to focus on the analysis instead of formatting.